Assessing primitives performance\\ on multi-stage execution

### 2018-05-08 paper.tex
ff
added appendix

@@

   \subcaption{Size 1000}
   \end{subfigure}
   \subcaption*{\textbf{LLVM-Mac results}}
    \end{subfigure}
   \label{fig:llvm}
\end{figure*}

%\cba{Je pense string de taille 0-1 c'est cool pour montrer que le code C va moins vite que pur smalltalk dans ce cas (si c'est vraiment le cas)}
We performed the benchmarks upon 4 different string sizes: 0, 5, 100 and 1000 characters, using 2 different compilers: GCC on one hand and LLVM on the other hand. Figure \ref{fig:gcc} and \ref{fig:llvm} show the results in terms of relative speed-up towards the baseline implementation\footnote{i.e. the pure Smalltalk version}, respectively for GCC and LLVM.

@@

%% Appendix
\appendix
\section{Appendix}

\cba{Source code et generated C and ASM code for all versions}

Text of appendix \ldots

>>>>

   \label{fig:gcc}

@@

   \subcaption{Size 1000}
   \end{subfigure}
   \subcaption*{\textbf{LLVM-Mac results}}
    \end{subfigure}
   \label{fig:bench}
\end{figure*}

%\cba{Je pense string de taille 0-1 c'est cool pour montrer que le code C va moins vite que pur smalltalk dans ce cas (si c'est vraiment le cas)}
We performed the benchmarks upon 4 different string sizes: 0, 5, 100 and 1000 characters, using 2 different compilers: GCC on one hand and LLVM on the other hand. Figure \ref{fig:bench} show the results in terms of relative speed-up towards the baseline implementation\footnote{i.e. the pure Smalltalk version}, respectively for GCC and LLVM.

@@

%% Appendix
\appendix
\section{Smart Syntax code}
\label{SmartSyntaxAppendix}

\cba{Source code et generated C code et generated ASM code}

\section{Slang Plugin code}
\label{SmartSyntaxAppendix}

\cba{Source code et generated C code et generated ASM code}

\section{Slang code}
\label{SlangAppendix}

\cba{Source code et generated C code et generated ASM code}

\section{Cog's RTL code}
\label{RTLAppendix}

\cba{Source code et generated ASM code}
